Rough calculations

### 2015-11-11 notes/pde-clines.Rmd

<!--
Therefore, assuming $G$ is sufficiently nice,
$$\begin{aligned}
\frac{d}{d\tau} g(x,z,a,b,\tau)
&=
G_{r(a,b)} g(x,z,a,b,\tau)
+
\int_a^b
\left(
    g(x,z,a,\theta,\tau)g(x,z,\theta,b,\tau) 
    - g(x,z,a,b,\tau)
\right)
d\theta
\end{aligned}$$
-->
Since $z \in \{A,B\}$, this is a system of two integro-differential equations 
in three variables plus time ($x$, $a$, $b$, and $\tau$; four if $x\in\R^2$).

>>>>

Therefore, assuming $g$ is sufficiently nice,
$$\begin{aligned}
\frac{d}{d\tau} g(x,z,a,b,\tau)
&=
G_{r(a,b)} g(x,z,a,b,\tau)
+
I g(x,z,a,b,\tau),
\end{aligned}$$
where $I$ is the integral operator defined above.
Since $z \in \{A,B\}$, this is a system of two integro-differential equations 
in three variables plus time ($x$, $a$, $b$, and $\tau$; four if $x\in\R^2$).

### 2015-11-11 notes/rough-calculations.Rmd

a.  The haplotype of a $B$ allele at distance $x$ into the $A$ side should be of length about $\sigma/(sx)$.

@@

a.  This is (probably) the Laplace transform of the time since the $B$ allele
    last had an ancestor on the $B$ side,
    i.e., for a $B$ lineage to make it back to the $B$ side.
    Since lineages on the wrong side move at speed $\sigma/s$,
    if the allele is at position $x$, 
    this will take about $sx/\sigma$;
    and so the haplotype should be about $\sigma/(sx)$.

>>>>

a.  The haplotype of a $B$ allele at distance $x$ into the $A$ side should be of length about $\sigma/(sx)$, as long as this is less than $1/\tau$. (this is fairly restrictive)

@@

a.  This is (probably) the Laplace transform of the time since the $B$ allele
    last had an ancestor on the $B$ side,
    i.e., for a $B$ lineage to make it back to the $B$ side.
    Since lineages on the wrong side move at speed $\sigma/s$,
    if the allele is at position $x$, 
    this will take about $sx/\sigma$;
    and so the haplotype should be about $\sigma/(sx)$.
    This gives the size of the chunk carried with it on this excursion;
    this will be of the same type with high probability at least if the length is less than $1/\tau$,
    as above.
